
%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%-----------HEADER-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\LARGE Jawahar Babu Selvaraj}} & Ottawa ON, Canada \\
{\Large Java Developer} & Mobile: (343) 987-9162 \\
\end{tabular*}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llll@{\extracolsep{\fill}}}
\href{mailto:jawaharbabu199914@gmail.com}{jawaharbabu199914@gmail.com} & 
\href{https://github.com/jawaharbabus/}{github.com/jawaharbabus/} &
\href{https://www.linkedin.com/in/jawahar-babu-s}{linkedin.com/in/jawahar-babu-s/} &
\href{https://jawaharbabu.me}{jawaharbabu.me} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Carleton University}{Sep 2023- Apr 2025}
{Master of Engineering in Software Engineering; CGPA: 3.67/4.0 (A)}{}
\resumeSubheading
{Government College of Technology - Anna University}{Aug 2017 - Apr 2021}
{Bachelor of Engineering in Electronics and Communications; CGPA: 8.63/10}{}
\resumeSubHeadingListEnd
\vspace{5pt}

%-----------SKILLS-----------------
\vspace{-5pt}
\section{Skills}
\resumeSubHeadingListStart
\resumeSubItem{Programming Languages}{Java, Python, JavaScript, SQL}
\resumeSubItem{Frameworks}{ReactJS, NodeJS, Spring, Flutter}
\resumeSubItem{Databases}{PostgreSQL, MongoDB, DynamoDB}
\resumeSubItem{DevOps \& Tools}{Git, Linux, Docker, Kubernetes, Jenkins, SonarQube}
\resumeSubItem{Other Skills}{Agile methodology, Microservices and Restful APIs, Software Testing and Automation, Database Modeling and Management, AWS Cloud}
\resumeSubHeadingListEnd
\vspace{5pt}
  
%-----------Experience-----------------
\vspace{-5pt}
\section{Experience}
%-----------SDE-----------------
\resumeSubHeadingListStart
    \resumeSubheading{Software Development Engineer}{July 2022 - July 2023}
    {Bosch Global Software Technologies}{}
    \resumeItemListStart
          {
\item Developed cross-platform software applications in Flutter for collection, processing, real time analysis and visualisation of sensor data, presented at CES 2023. Collaborated with German sensor and algorithm developers during an on-site business trip, enhancing international teamwork and product requirement alignment.
  \item Engineered interfaces between C Algorithms and Flutter applications, achieving a 35\% reduction in communication lag for 16kHz high-frequency data.
  \item Developed a custom Bluetooth Communication plugin in Flutter, reducing data transfer latency by 25\%. I was awarded the title "Extra Miler" for my out-of-the-box approach in the development and delivery of the plugin.
  \item  Decomposed a large monolithic application into a modular Unified App Framework (UAF) consisting of reusable components, reducing code duplication by 40\% and development time for dependent applications by 30\%. 
   \item Designed and maintained CI/CD pipelines in Jenkins, incorporating unit testing, integration testing, static code analysis, linting, and automated deployment with SonarQube integration, leading to a reduction in deployment time by 40\% and code smells by 30\%..

}      \resumeItemListEnd
\vspace{-1pt}

%-----------SDET-----------------
    \resumeSubheading
		{Software Development Engineer in Test}{July 2021 - June 2022}
		{Bosch Global Software Technologies}{}
		\resumeItemListStart
        \item Conducted UI/UX testing for mobile and web applications with platform-specific testcases. Interacted with different development teams to design suitable test plans to thorough application's performance analysis.
        \item Spearheaded an Automated testing library in Python, reducing testing time by 75\%. I was awarded the title "The Best Tyro" for my initiative.
        \item Created and performed Unit, Widget and Integration tests for Flutter applications that increased overall code coverage by 40\%.
        \item Performed static and dynamic code analysis using tools like Clang and Sonarqube to identify bugs, code smells and code complexity.
	\resumeItemListEnd
    \vspace{-1pt}
    
%-----------PROJECT TRAINEE-----------------
 %    \resumeSubheading
	% 	{Project Trainee}{March 2021 - June 2021}
	% 	{Bosch Global Software Technologies}{}
	% 	\resumeItemListStart
 %        \item{Developed a Deep learning image classifier in Python to detect defective sensors and to automate manual sensor inspection, thereby speeding up the manufacturing process.}
 %        \item{Trained a variational autoencoder-based semi-supervised model with image processing techniques in TensorFlow to build a state-of-the-art classifier with 92\% accuracy.}
	% \resumeItemListEnd
% \vspace{-1pt}

%-----------INTERNSHIP-----------------
\resumeSubheading{Intern in Full stack Web Development}{January 2021 - March 2021}
   {Pinesphere Solutions} {}
    \resumeItemListStart                
          {
    \item Built a cloud-native Home Automation Web Application, allowing clients to interact with home appliances in real-time, utilizing a ReactJS frontend and Spring Boot APIs with MongoDB for data persistence.
  \item Gained practical experience in designing scalable microservices, building RESTful APIs, and deploying applications using AWS services.
  }
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{5pt}

%-----------Personal Projects--------
% \vspace{-5pt}
% \section{Projects}
% \resumeSubHeadingListStart
%    \resumeSubheading
%     {\href{https://github.com/jawaharbabus/jakartaee-examples/tree/feature/app/jakarta-shop-bot/ms1/applications/JakartaShopBot} {JakartaShopBot - OpenSource Contribution}}{June 2024 - Present}
%    {Jakarta Enterprise Edition (EE)} {}
%     \resumeItemListStart
%           {
%   \item Currently involved in designing and implementing an e-commerce chatbot application using JEE technologies such as JSF, Websockets, CDI, and Langchain4j with OpenAI APIs in GlassFish Server, enhancing user interaction and support.
% }      \resumeItemListEnd
% \vspace{-1pt}
% \resumeSubHeadingListEnd
% \vspace{5pt}

%-----------CERTIFICATIONS-----------------
\vspace{-5pt}
\section{Certifications}
\resumeSubHeadingListStart
\vspace{5pt}
\resumeSubheading {\href{https://www.credly.com/badges/c2c11be3-5f0e-4b30-b665-50f81b7231b8/public_url}{AWS Certified Cloud Practioner}}{November 2024}{Amazon Web Services}{}
\resumeItemListStart
  \item Acquired knowledge of AWS services such as EC2, Lambda, API Gateway, and DynamoDB, with a focus on serverless design principles, scalability, and monitoring.
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}



%-----------Awards-----------------
% \vspace{-5pt}
% \section{Accomplishments}
% \begin{description}[font=$\bullet$]

% \item {“Best Tyro” awarded by my manager at Bosch for my exceptional performance and new initiatives in my workplace as a beginner. (2022)}
% \item {“Extra Miler” awarded by my tech lead at Bosch for going out of my project scope, supporting in development and delivery of Web BLE Plugin. (2023)}
% \item one of the youngest to make a Business trip to the headquarters at Stuttgart, Germany to work on a project in collaboration with algorithm developers (2023).

% \item Was a part of the development team for a mobile application which was presented at CES, Las Vegas on behalf of Bosch SensorTec (2022). 

% \end{description}
% \vspace{5pt}