%-----------Experience-----------------
\vspace{-5pt}
\section{Experience}
%-----------SDE-----------------
\resumeSubHeadingListStart
    \resumeSubheading{Software Development Engineer}{July 2022 - July 2023}
    {Bosch Global Software Technologies}{}
    \resumeItemListStart
          {
\item Developed cross-platform web applications in Flutter for collection, processing, real time analysis and visualisation of sensor data, presented at CES 2023. Collaborated with German sensor and algorithm developers during an on-site business trip, enhancing international teamwork and product requirement alignment.
  \item Engineered interfaces between C Algorithms and Flutter applications, achieving a 35\% reduction in communication lag for 16kHz high-frequency data.
  \item Developed a custom Bluetooth Communication plugin in Flutter, reducing data transfer latency by 25\%. I was awarded the title "Extra Miler" for my out-of-the-box approach in the development and delivery of the plugin.
  \item  Decomposed a large monolithic application into a modular Unified App Framework (UAF) consisting of reusable components, reducing code duplication by 40\% and development time for dependent applications by 30\%. 
   \item Designed and maintained CI/CD pipelines in Jenkins, incorporating unit testing, integration testing, static code analysis, linting, and automated deployment with SonarQube integration, leading to a reduction in deployment time by 40\% and code smells by 30\%.

}      \resumeItemListEnd
\vspace{-1pt}

%-----------SDET-----------------
    \resumeSubheading
		{Software Development Engineer in Test}{July 2021 - June 2022}
		{Bosch Global Software Technologies}{}
		\resumeItemListStart
        \item Conducted UI/UX testing for mobile and web applications with platform-specific testcases. Interacted with different development teams to design suitable test plans to thorough application's performance analysis.
        \item Spearheaded an Automated testing library in Python, reducing testing time by 75\%. I was awarded the title "The Best Tyro" for my initiative.
        \item Created and performed Unit, Widget and Integration tests for Flutter applications that increased overall code coverage by 40\%.
        \item Performed static and dynamic code analysis using tools like Clang and Sonarqube to identify bugs, code smells and code complexity.
	\resumeItemListEnd
    \vspace{-1pt}

%-----------INTERNSHIP-----------------
\resumeSubheading{Intern in Full stack Web Development}{January 2021 - March 2021}
   {Pinesphere Solutions} {}
    \resumeItemListStart                
          {
    \item Built a cloud-native Home Automation Web Application, allowing clients to interact with home appliances in real-time, utilizing a ReactJS frontend and ExpressJS backend with MongoDB for data persistence.
  \item Gained practical experience in designing scalable microservices, building RESTful APIs, and deploying applications using AWS services.
  }
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{5pt}

