%-----------Experience-----------------
\vspace{-5pt}
\section{Experience}
%-----------SDE-----------------
\resumeSubHeadingListStart
    \resumeSubheading{Software Development Engineer}{July 2022 - July 2023}
    {Bosch Global Software Technologies}{}
    \resumeItemListStart
          {
\item Developed cross-platform software applications in Flutter for collection, processing, real time analysis and visualisation of sensor data, presented at CES 2023. Collaborated with German sensor and algorithm developers during an on-site business trip, enhancing international teamwork and product requirement alignment.
  \item Developed a custom Bluetooth Communication plugin in Flutter, reducing data transfer latency by 25\%. I was awarded the title "Extra Miler" for my out-of-the-box approach in the development and delivery of the plugin.
  \item  Decomposed a large monolithic application into a modular Unified App Framework (UAF) consisting of reusable components, reducing code duplication by 40\% and development time for dependent applications by 30\%. 
   \item Designed and maintained CI/CD pipelines in Jenkins, leveraging Python scripts to automate development and delivery workflows leading to a reduction in deployment time by 40\% and code smells by 30\%.


}      \resumeItemListEnd
\vspace{-1pt}

%-----------SDET-----------------
    \resumeSubheading
		{Software Development Engineer in Test}{July 2021 - June 2022}
		{Bosch Global Software Technologies}{}
		\resumeItemListStart
        \item Spearheaded an Automated testing library in Python, reducing testing time by 75\%. I was awarded the title "The Best Tyro" for my initiative.
        \item Conducted UI/UX testing for mobile and web applications with platform-specific testcases. Interacted with different development teams to design suitable test plans to thorough application's performance analysis.
        \item Created and performed Unit, Widget and Integration tests for Flutter applications that increased overall code coverage by 40\%.
	\resumeItemListEnd
    \vspace{-1pt}
    
% -----------PROJECT TRAINEE-----------------
    \resumeSubheading
		{Project Trainee}{March 2021 - June 2021}
		{Bosch Global Software Technologies}{}
		\resumeItemListStart
        \item Built an image classification tool in Python using OpenCV and TensorFlow to detect defective sensors, automating the inspection process and improving manufacturing efficiency.
        \item Leveraged machine learning models and Python libraries such as NumPy, Pandas, Scikit-learn, and Matplotlib to enhance defect detection accuracy to 92\%, achieving reliable results for production environments.
	\resumeItemListEnd
\vspace{-1pt}

%-----------INTERNSHIP-----------------
\resumeSubheading{Intern in Full stack Web Development}{January 2021 - March 2021}
   {Pinesphere Solutions} {}
    \resumeItemListStart                
          {
    \item Built a cloud-native Home Automation Web Application, allowing clients to interact with home appliances in real-time, utilizing a ReactJS frontend and FastAPI backend with MongoDB for data persistence.
  \item Gained practical experience in designing scalable microservices, building RESTful APIs, and deploying applications using AWS services.
  }
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{5pt}

